---
title: "Activity: Nuclear Reactors"
author: "Daniel Gao"
output: html_notebook
---

```{r}
library(tidyverse)
library(lubridate)
```

## Scrape the Data 

```{r}
#My code here.... 
library(rvest)

page <- "https://en.wikipedia.org/wiki/List_of_commercial_nuclear_reactors#"
tableList <- page %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)
 
japan <-
  (tableList[[21]][-1 , 1:9]) %>%
  rename(name = Plantname, 
         reactor = `UnitNo.`,
         model = Type,
         status = Status, 
         netMW = `Capacity(MW)`,
          construction = Beginbuilding,
         operation = `Commercialoperation`, 
         closure = Closed) 
japan %>%
  mutate(reactor = as.integer(reactor), 
         netMW = as.integer(netMW),
         operation = dmy(operation),
         closure = dmy(closure),
         construction = dmy(construction)) %>%
  head()

```


## Your turn: In what ways is the table tidy? How is it not tidy? What’s different about it from a tidy table?

My answer here..... 
This data is tidy as each variable has its own column, each case has its own row, and each value has its own cell.

## Your Turn: Plot Net Generation Capacity vs Construction Date

```{r}
#my code here 
japan %>%
  ggplot(aes(x = netMW, y = construction )) +
  geom_point(shape = "circle", size = 1) +
  xlab("Net Generation Capacity") +
  ylab("Construction Date")
```


## Your Turn: Scrape & Clean China Data (then merge with Japan)

```{r}
#my code here... 
china <- (tableList[[10]][-1 , 1:9]) %>%
  rename(name = Plantname, 
         reactor = `UnitNo.`,
         model = Type,
         status = Status, 
         netMW = `Capacity(MW)`,
          construction = Beginbuilding,
         operation = `Commercialoperation`, 
         closure = Closed) 
china %>%
  mutate(reactor = as.integer(reactor), 
         netMW = as.integer(netMW),
         operation = dmy(operation),
         closure = dmy(closure),
         construction = dmy(construction)) %>%
  head()
chinajapan <- rbind(china, japan) 
chinajapan %>% 
  head()

```



## Your Turn: Reconstruct Info Graphic of Japan Reactors (or other country of interest)

```{r}
#My code here

japan %>%
  ggplot(aes(x = operation, y = name)) +
  geom_segment(aes(x = construction, xend = operation, yend = name, color = model, size = status, shape = status)) 
```
